### 2014-11-07 docs/ms.Rmd
Got example ref working (see abstract) - I'll do the rest when it's not Friday night. Also moved styling to .sty file

---
fontsize: 12pt
geometry: margin=0.75in
output: pdf_document
---

#The transparency of methods-reporting in studies measuring biological colouration

@@

##Abstract

##Introduction
Since Thayer (1909), Poulton (1890) and Wallace (YEAR) generations of biologists have endeavored to explain the mechanisms and functions of animal and plant coloration. For these biologists, identifying best practice in measuring color and color pattern and in determining how other species see colour has been a great challenge. Over the past 150 years biologists, both independently and in collaboration with physicists and chemists, have developed a range of techniques used to measure and analyse animal and plant coloration including spectrophotometry (also called spectroradiometry, spectroscopy ETC), photography and visual modeling.

@@

##Ideal reporting in colour studies

@@

##What is reporting like in the literature?

@@

>>>>

# The transparency of methods-reporting in studies measuring biological colouration

@@

## Abstract

TEST REFERENCE [@endler_comparing_2005; @endler_convergent_1982]

## Introduction
Since Thayer (1909), Poulton (1890) and Wallace (YEAR) generations of biologists have endeavored to explain the mechanisms and functions of animal and plant coloration. For these biologists, identifying best practice in measuring color and color pattern and in determining how other species see colour has been a great challenge. Over the past 150 years biologists, both independently and in collaboration with physicists and chemists, have developed a range of techniques used to measure and analyse animal and plant coloration including spectrophotometry (also called spectroradiometry, spectroscopy ETC), photography and visual modeling.

@@

## Ideal reporting in colour studies

@@

## What is reporting like in the literature?

@@

## References
